---
title: "Madrasa Survey Final"
author: "Rafeel Wasif"
date: "January 12, 2017"
output: html_document
---


```{r results=FALSE, warning=FALSE, comment=FALSE, warning=FALSE, error = FALSE, message=FALSE}
rm(list=ls())

library(corrplot)
library(xtable)
library(foreign)
library(dplyr)
library(stargazer)
library(doBy)
library(htmlTable)
library(ggplot2)
library(lsr)
library(plotrix)
library(descr)
```




```{r, warning=FALSE}


data <- read.spss("Data.sav")
data <- as.data.frame(data)
```


Making different groups of data based on the treatment.

```{r}

groups <- list()
for (i in 1:5) {
  data$group <- as.numeric(data$group)
  groups[[i]] <- data %>%
    filter(group == i)
}


control <- groups[[1]]
government <- groups[[2]]
saudi_arab <- groups[[3]]
USA <- groups[[4]]
germany <- groups[[5]]



```
Running Wilcox test results to find if the mean of our treatment result is significantly different the mean of our other treatments.

Wilcox Test Results

```{r}

wilcox_test_list <- list(control, government, saudi_arab, USA, germany)
wilcox_test_results <- list()
for (i in 1:5) {
  wilcox_test_results[[i]] <- wilcox.test(as.numeric(control$group_result), as.numeric(wilcox_test_list[[i]]$group_result))

}



```



Confirming whether my variable coding is correct for subsequent analysis.

```{r}
# Support is 1
table(control$q6, as.numeric(control$q6))

# Male is 1
table(control$Gender, as.numeric(control$Gender))

table(control$q5, as.numeric(control$q5))

```

Binding the Wilcox test results together.





Forming Sub-groups within the treatment groups.

```{r}

sub_groups_pml <- list()
sub_groups_male <- list()
support_military <- list()

for (i in 1:5) {

    sub_groups_pml[[i]] <- wilcox_test_list[[i]] %>%
    filter(as.numeric(q5) == 1)

    sub_groups_male[[i]] <- wilcox_test_list[[i]] %>%
    filter(as.numeric(Gender) == 1)
    
    support_military[[i]] <- wilcox_test_list[[i]] %>%
    filter(as.numeric(q6) == 1)
    
    
    
    }
  


```



Converting the groups results into Dichotomous variable. Willingness to donate likert scale higher or equal to 3 is 1 on the dichotomous scale. 


```{r}

data_dichotom <- mutate(data, Will_Donate = ifelse(as.numeric(group_result) >= 3, 1, 0)) %>% mutate(punjabi = ifelse(as.numeric(d9) ==1, 1,0 )) 


# Double-checking the results.

table(data_dichotom$Will_Donate, data_dichotom$d9)


```


Running the Dichotomous Group Result.

```{r, results = "hide"}
data_dichotom$group <- as.factor(data_dichotom$group)


```




Running the regression without the ethnicity variable as there is not enough variation in the ethnicity variable and our model BiC improves.




```{r}

# Forming sub-groups of data. For cleaning purpose I make them again.
Pml_group <- data_dichotom %>% filter(as.numeric(q5) == 1)
Military_group <- data_dichotom %>% filter(as.numeric(q6) == 1)
Male_Group <- data_dichotom %>% filter(as.numeric(Gender) == 1)

Groups_List <- list(Pml_group, Military_group, Male_Group)

```


Finding CohensD, the effect size.

```{r}
cohens_d_list <- list(control, government, saudi_arab, USA, germany)

cohen_sd <- list()
for (i in 2:5) {
cohen_sd[[i]] <-   cohensD(as.numeric(cohens_d_list[[1]]$group_result), as.numeric(cohens_d_list[[i]]$group_result))
} 

cohen_sd_set <- do.call(rbind, cohen_sd)
cohen_sd_will_donate <- list()

# Cohens D for Scale of Dichotmous scale.

for (i in 2:5) {
cohen_sd_will_donate[[i]] <-   cohensD(as.numeric(cohens_d_list[[1]]$will), as.numeric(cohens_d_list[[i]]$group_result))
} 

```



Making Table of Variable Means and SD.




```{r}


data_dem_cols <- c("d2", "d3", "d4",  "d7", "d8a","group" )

data_dem <- data[data_dem_cols]
government_dem <- government[data_dem_cols]
control_dem <- control[data_dem_cols]
saudi_dem <- saudi_arab[data_dem_cols]
us_dem <- USA[data_dem_cols]
germany_dem <- germany[data_dem_cols]


dem_means <- list()
mean_covariates_list <- list(control_dem, government_dem, saudi_dem, us_dem, germany_dem)


for (i in 1:5)
{
  dem_means[[i]] <- colMeans(sapply(mean_covariates_list[[i]], as.numeric))
  
}

dem_means_set <- as.data.frame(do.call(rbind, dem_means))[,-6] 

rownames(dem_means_set) <- c("Control", "Government", "Saudi Arab", "USA", "Germany")
colnames(dem_means_set) <- c("Total HH Income", "Work Sector", "Lived Outside Pakisan","Highest Education Level", "Marital Status")

round_df <- function(x, digits) {
    # round all numeric variables
    # x: data frame 
    # digits: number of digits to round
    numeric_columns <- sapply(x, mode) == 'numeric'
    x[numeric_columns] <-  round(x[numeric_columns], digits)
    x
}



dem_means_set <- round_df(0.199, 2)
dem_means_set <- t(dem_means_set)
htmlTable(dem_means_set)
```







```{r}


levels(data_dichotom$q4)


data_dichotom$madrasa_enrolment <- data_dichotom$q4

levels(data_dichotom$madrasa_enrolment)[levels(data_dichotom$madrasa_enrolment)=="Yes, I was enrolled in the past, but I am not enrolled at present"  ] <- "Yes"

levels(data_dichotom$madrasa_enrolment)[levels(data_dichotom$madrasa_enrolment)=="Yes, I am currently enrolled"  ] <- "Yes"



levels(data_dichotom$madrasa_enrolment)[levels(data_dichotom$madrasa_enrolment)=="Refused"  ] <- "No, I have not enrolled, and do not plan to enroll in the future"


levels(data_dichotom$madrasa_enrolment)[levels(data_dichotom$madrasa_enrolment)=="Dont know"  ] <- "No, I have not enrolled, and do not plan to enroll in the future"


levels(data_dichotom$madrasa_enrolment)[levels(data_dichotom$madrasa_enrolment)=="No, I have not enrolled, and do not plan to enroll in the future"  ] <- "No"


table(data_dichotom$q4, data_dichotom$madrasa_enrolment)
```


```{r}

data_dichotom$family_madrasa <- data_dichotom$q3

levels(data_dichotom$family_madrasa)[levels(data_dichotom$family_madrasa)=="Prefer to Not Respond"  ] <- "No"


levels(data_dichotom$family_madrasa)[levels(data_dichotom$family_madrasa)=="Yes, but not at present"] <- "Yes, they are currently enrolled"

levels(data_dichotom$family_madrasa)[levels(data_dichotom$family_madrasa)=="Yes, they are currently enrolled"] <- "Yes"



levels(data_dichotom$family_madrasa)[levels(data_dichotom$family_madrasa)=="Yes, they are currently enrolled"] <- "Yes"



```



Making List of Covariates.

```{r}

labels_list_new <- c('Goverment', 'Saudi Arabia', 'USA', 'Germany', 'Madrasa Donation in Last 12 months No',  'Madrasa Donation in Last 12 months -Dont Know',  'Madrasa Donation in Last 12 months -Prefer to Not Respond', 'Family Members in Madrasa- Currently enrolled', 'Family Members in Madrasa- Not Currently Enrolled', 'Family Members in Madrasa -Prefer to Not Respond', 'Extended Family in Madrasa-No' ,  'Enrolled in Madrasa -Yes I want to get enrolled in the future', 'Enrolled in Madrasa- No',  'Political Party- Pakistan Tehreek-e-Insaf' , 'Political Party-Pakistan Peoples Party', 'Political Party -None' , 'Political Party - Refused to Answer', 'Political Party -Dont know',  'Military Operation Against Taliban- Unnecessary' , 'Military Operation Against Taliban- Refused to Answer', 'Military Operation Against Taliban -Dont know', 'Female', 'Age', 'Married', 'Divorced', 'Highest Education Level', 'Not Lived Outside Pakistan', 'Agriculture',  'Service Industry',  'Informal Sector',  'Student',  'Refused', 'Rs 5001-Rs 11000', 'Rs 11001 -Rs 14000', 'Rs 14001 -Rs 16000', 'Rs 16001 - Rs 20000' , 'Rs 20001 -Rs 37000', 'More than Rs 37000', 'Rural' )






```



Binary Logit Regression

```{r}

regression_model_1_no_ethnicity_madrasa_enrolment_family <-  glm(Will_Donate ~ group, family = binomial, data = data_dichotom)
regression_model_2_no_ethnicity_madrasa_enrolment_family <- glm(Will_Donate ~ group  + Gender + Age + d8a + d7 + d4 + d3 + d2 + ur 
, family = binomial, data = data_dichotom)


regression_model_3_no_ethnicity_madrasa_enrolment_family <-  glm(Will_Donate ~ group + q1 + q2 + family_madrasa + madrasa_enrolment + q5 + q6, data = data_dichotom 
, family = binomial)


regression_model_4_no_ethnicity_madrasa_enrolment_family <-  glm(Will_Donate ~ group + q1 + q2 + family_madrasa + madrasa_enrolment + q5 + q6  + Gender + Age + d8a + d7 + d4 + d3 + d2 + ur, data = data_dichotom , family = binomial)

summary(regression_model_4_no_ethnicity_madrasa_enrolment_family)

stargazer(regression_model_1_no_ethnicity_madrasa_enrolment_family, regression_model_2_no_ethnicity_madrasa_enrolment_family, regression_model_3_no_ethnicity_madrasa_enrolment_family, regression_model_4_no_ethnicity_madrasa_enrolment_family, out = "regression_complete_ethnicity_madrasa_enrolment_family.html", covariate.labels = labels_list_new)








```

Probit regression with scale 1-5.

```{r}

probit_regression_model_1_no_ethnicity_madrasa_family <-  glm(group_result ~ group, family=binomial(link="probit"), data = data_dichotom)
probit_regression_model_2_no_ethnicity_madrasa_family <- glm(group_result ~ group  + Gender + Age + d8a + d7 + d4 + d3 + d2 + ur 
, family=binomial(link="probit"), data = data_dichotom)


probit_regression_model_3_no_ethnicity_madrasa_family <-  glm(group_result ~ group + q1 + q2 + family_madrasa + madrasa_enrolment + q5 + q6, data = data_dichotom 
, family=binomial(link="probit"))


probit_regression_model_4_no_ethnicity_madrasa_family <-  glm(group_result ~ group + q1 + q2 +  family_madrasa + madrasa_enrolment + q5 + q6  + Gender + Age + d8a + d7 + d4 + d3 + d2 + ur, data = data_dichotom , family=binomial(link="probit"))

summary(probit_regression_model_4_no_ethnicity_madrasa_family)

table(data_dichotom$q3, data_dichotom$group_result)
table(data_dichotom$d8a)
stargazer(probit_regression_model_1_no_ethnicity_madrasa_family, probit_regression_model_2_no_ethnicity_madrasa_family, probit_regression_model_3_no_ethnicity_madrasa_family, probit_regression_model_4_no_ethnicity_madrasa_family, out = "probit_regression_complete_ethnicity_madrasas_family_labels_final.html", covariate.labels = labels_list_new)


```


Collecting information about the frequency of different responses that individuals gave.

```{r}
print.xtable(xtable(table(data_dichotom$group_result)), type = "html", file="group_results.html")


```
Cross-Tables of Willingness to Donate with group and donations in the last 12 months.

```{r}

CrossTable(data_dichotom$Will_Donate, data_dichotom$group, dnn = c("Willingness to Donate", "Group"))

round(CrossTable(data_dichotom$Will_Donate, data_dichotom$q1, dnn = c("Willingness to Donate", "Previous Donations in Last 12 Months"),2)

CrossTable(data_dichotom$group_result, data_dichotom$q1, dnn = c("Willingness to Donate", "Previous Donations in Last 12 Months"))

CrossTable(data_dichotom$group_result, data_dichotom$group, dnn = c("Willingness to Donate", "Previous Donations in Last 12 Months"))

round(0.296,2)


round(prop.table(table(data_dichotom$Will_Donate, data_dichotom$group)),2)
)

```


Printing Wilcox Test Table

```{r}

wilcox_test_list <- list(control, government, saudi_arab, USA, germany)
wilcox_test_results <- list()
for (i in 1:5) {
  wilcox_test_results[[i]] <- wilcox.test(as.numeric(control$group_result), as.numeric(wilcox_test_list[[i]]$group_result))

}

wilcox_test_set <- do.call(rbind,wilcox_test_results)


wt_results <- cbind.data.frame(c("Control",  "Government", "Saudi Arabia", "USA", "Germany"), do.call(rbind, wilcox_test_set[,"p.value"]))
wt_results <- wt_results[-1,]
colnames(wt_results) <- c("Treatment", "Result")
wt_results[,"Result"] <- round(as.numeric(wt_results[,"Result"]),5)
print(xtable(wt_results), type = "html", file = "wt.html")

```


